Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2013-11-07 writeups/proposal/proposal.tex
foo
Former-commit-id: 436ee89efb7c5e4719da38f8f64d99f9dd982524 [formerly 0976639a46d10fc7273de09316fe5c8aac3bbeb7]
Former-commit-id: 35277e3edcf4bc36f851eaf51ad1bced624fb82a

Lucene \parencite{McCandless2010} is a commonly-used open-source software tool that measures the similarity between a query and candidate documents in a database.
It uses the term frequency--inverse document frequency co-occurrence measure to quantify the similarity between a word in the query and a possible document to retrieve.

>>>>

Lucene \parencite{McCandless2010} is a commonly-used open-source software tool that measures the similarity between a query and candidate documents in a database.
It uses the term frequency---inverse document frequency co-occurrence measure to quantify the similarity between a word in the query and a possible document to retrieve.
